---
title: "RDS-Problems"
author: "JingjianGao"
date: "2022-10-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 12.2.1.2
Compute the rate for table2, and table4a + table4b. You will need to perform four operations:

Extract the number of TB cases per country per year.
Extract the matching population per country per year.
Divide cases by population, and multiply by 10000.
Store back in the appropriate place.
Which representation is easiest to work with? Which is hardest? Why?

```{r}
library(tidyverse)
data("table2")
table2_cases <- filter(table2,type=="cases") %>%
  rename(cases=count)%>%
  arrange(country,year)

table2_population <- filter(table2,type=="population") %>%
  rename(population=count) %>%
  arrange(country,year)

table2_cases_population_ratio <- tibble(
  year=table2_cases$year,
  country=table2_cases$country,
  cases=table2_cases$cases,
  population=table2_population$population
) %>%
  mutate(cases_population_ratio=cases/population*10000) %>%
  select(country,year,cases_population_ratio)

table2_cases_population_ratio <-table2_cases_population_ratio %>%
  mutate(type="cases_population_ratio")%>%
  rename(count=cases_population_ratio)

new_table2 <- bind_rows(table2,table2_cases_population_ratio) %>%
    arrange(country, year, type, count)

data("table4a")
data("table4b")
table4_ab <-  tibble(country = table4a$country,
                     `1999` = table4a[["1999"]] / table4b[["1999"]] * 10000,
                     `2000` = table4a[["2000"]] / table4b[["2000"]] * 10000
)


#As you can see from the code, I think table2 is hard to work with. Table4a and
#table4b are much easier to handle.
                        
```


## 12.2.1.3
Recreate the plot showing change in cases over time using table2 instead of table1. 
What do you need to do first?

```{r}
table2 %>%
  filter(type == "cases") %>%
  ggplot(aes(year, count)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))+
  ylab("Cases")

```

## 12.3.3.1
Why are pivot_longer() and pivot_wider() not perfectly symmetrical?
Carefully consider the following example:

stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks %>% 
  pivot_wider(names_from = year, values_from = return) %>% 
  pivot_longer(`2015`:`2016`, names_to = "year", values_to = "return")

Hint: look at the variable types and think about column names.)
pivot_longer() has a names_ptypes argument, e.g.  names_ptypes = list(year = double()). What does it do?


```{r}
#They are not perfectly symmetrical because the column type information is missing when we transform the dataframe
#Character, Numeric type differences, etc


```

## 12.3.3.2
Why does this code fail?

table4a %>% 
  pivot_longer(c(1999, 2000), names_to = "year", values_to = "cases")
#> Error: Can't subset columns that don't exist.
#> Locations 1999 and 2000 don't exist.
#> There are only 3 columns.


```{r}
#This code fails because the function interprets 1999 and 2000 to be 1999th and 2000th column instead of numbers. Thus location 1999 and 2000 don't exist. We need to have (').


```

## 12.3.3.3
What would happen if you widen this table? Why? How could you add a new column to uniquely identify each value?


```{r}
people <- tribble(
  ~name,             ~names,  ~values,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)
pivot_wider(people, names_from="name", values_from = "values")

#If we widen this table, then it will return error because name and names columns do not uniquely identify rows.
#We can add a new column showing the unique combination of name and names.


```


## 12.3.3.4
Tidy the simple tibble below. Do you need to make it wider or longer? What are the variables?

```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
tidy_preg <- preg %>%
    pivot_longer(c(male, female), names_to = "sex", values_to = "count",values_drop_na = TRUE)
tidy_preg

#We need to make it longer. The variables are sex, pregnant, and number of observations

```
